---
title: "Lab 9"
author: "Kristina Arevalo"
date: '`r format(Sys.time(), "%a %b %d %Y")`'
output: 
  pdf_document:
    latex_engine: xelatex
    toc: yes 
    toc_depth: 2
monofont: Times New Roman
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE)
```

```{r,echo=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(readxl)
library(papaja)
```

\newpage

# Problem 1

Your task is to obtain the data from the following paper and conduct a reproducible analysis of their results.
Rosenbaum, D., Mama, Y., & Algom, D. (2017). Stand by Your Stroop: Standing Up Enhances Selective Attention and Cognitive Control. Psychological science, 28(12), 1864-1867.


The re-analysis should focus only on Experiment 3. There are three main goals

Reproduce as much of the analysis as possible using only paired-sample t-tests. Note, the authors reported a 2x2 repeated measures ANOVA, but consider how the same questions could be answered by t-tests (2 points)

```{r}
data <- read.csv("open_data/stroop_stand.csv")
```
     
## Sit Stroop effect
```{r}
(sit_stroop <- t.test(data$incongruent_sit,
                      data$congruent_sit,
                      paired = TRUE))
```

## Stand Stroop effect
```{r}
(stand_stroop <- t.test(data$incongruent_stand,
                        data$congruent_stand,
                        paired = TRUE))
```
 
Rosenbaum et al., (2017) reported "The Stroop effects in both the sitting condition, M = 118.9 ms, t(49) = 16.52, p < .01, d = 2.376, and the standing condition, M = 95.9 ms, t(49) = 14.327, p < .01, d = 2.034, were highly reliable."


We were able to reproduce the results of this paper. zwe found the Stroop effects in both the sitting condition, `r apa_print(sit_stroop)$full_result`, and the standing condition, `r apa_print(stand_stroop)$full_result`, were highly reliable.

Confidence = 100

# Problem 2 
Reproduce a graph of the means, like shown in the paper (2 points)
```{r}
data.long<- data %>%
  pivot_longer(cols = 1:4,
               names_to = c("Congruency","Posture"),
               names_sep = "_",
               values_to = "RTs")

overall_means <- data.long %>%
                  group_by(Posture,Congruency) %>%
                  summarise(meanRT = mean(RTs),
                            SEMRT = (sd(RTs)/sqrt(length(RTs))))

ggplot(overall_means, aes(x=Posture, y=meanRT, group=Congruency,fill=Congruency))+
  geom_bar(stat="identity",position="dodge")+
  theme_classic(base_size=12)+
  ylab("Mean Reaction Time (ms)")+
  geom_errorbar(aes(ymin=meanRT-SEMRT,
                    ymax=meanRT+SEMRT),
                position=position_dodge(width=0.9),
                width=.2,
                color="black")+
  coord_cartesian(ylim=c(500,1000))
```
Confidence = 50 
VERY thankful for your demonstration on wide to long, I've been using a different function (melt) to convert and sometimes it just messes it up so I end up using SPSS to restructure my data, but this way is so much better! Thank you!

# Problem 3
Present a power-curve analysis for the design. (2 points)
```{r}
effect_sizes <- seq(0,1.5,.1)

prop_significant <-c()
for(i in 1:length(effect_sizes)){
  sim_ps <- replicate(1000, t.test(replicate(50, rnorm(1, effect_sizes[i], 1)),
                                   mu = 0)$p.value)
  
  prop_significant[i] <- length(sim_ps[sim_ps < .05])/1000
}
plot_df <- data.frame(effect_sizes,
                      prop_significant)
ggplot(plot_df, aes(x=effect_sizes,y=prop_significant))+
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks=seq(0,1.5,.1))+
  scale_y_continuous(breaks=seq(0,1,.1)) +
  ylab("Proportion Significant")
```

Confidence = 0 




