---
title: "Lab 4"
author: "Kristina Arevalo"
date: '`r format(Sys.time(), "%a %b %d %Y")`'
output: 
  pdf_document:
    toc: yes 
    toc_depth: 2
monofont: Times New Roman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE)
```

```{r,echo=FALSE}
library(dplyr)
library(ggplot2)
```

\newpage

# Problem 1

Estimate the letter occurrence probabilities of all 26 letters in English by measuring a paragraph of English text from wikipedia. (hint use strsplit() to split a paragraph into individual letters) (1 point).
```{r}
my_paragraph <- "Microorganisms include all unicellular organisms and so are extremely diverse, living in almost every habitat, with some adapted to extremes such as very hot or very cold conditions, others to high pressure, and a few, such as Deinococcus radiodurans, which are adapted to high-radiation environments. Microorganisms also make up the microbiota found in and on all multicellular organisms. There is evidence that 3.45-billion-year-old Australian rocks once contained microorganisms, the earliest direct evidence of life on Earth. Microbes are important in human culture and health in many ways, serving to ferment foods and treat sewage, and to produce fuel, enzymes, and other bioactive compounds. This low-temperature electron micrograph shows a cluster of E. coli bacteria, magnified 10,000 times."

the_letters <- unlist(strsplit(my_paragraph, split = ""))
wiki <- tolower(the_letters)
letter_counts <- table(wiki)
letter_counts <- data.frame(letter_counts)

letters_only <- letter_counts %>% 
  filter(wiki %in%letters == TRUE)

total_letters <- sum(letters_only$Freq)

letters_only2 <- letters_only %>% 
  mutate(prob = Freq/total_letters)

letters_only2 %>% head()
```
Confidence: 50 needed to look into the video for some help

# Problem 2

Generate “random” strings of letters that are sampled from a distribution where letter occurrence probability is the same as natural English. Use the probabilities for each letter from this wikipedia article, or use your own estimates from the previous question (2 points).

```{r}

my_letters <- sample(letters_only2$wiki,50*5,replace=TRUE, prob = letters_only2$prob)

my_strings <- matrix(my_letters, ncol=5)

paste(my_strings[1,], collapse="")

random_strings <-c()
for(i in 1:dim(my_strings)[1]){
  random_strings[i] <- paste(my_strings[i,], collapse="")
}

random_strings
```
Confidence = 0

# Problem 3

Generate a random walk of 10,000 steps. In a random walk, you are simulating the process of randomly taking a step up or down, as if you are on an infinite staircase. At each step you flip a coin. If you get heads you go up one step, if you get tails you go down one step. Start on step 0, then simulate a random walk for 10,000 steps. Your vector should preserve the step number for each step. For example, if the the first three steps were all heads, then the vector would begin with 0,1,2,3, which indicates a single step up each time. Plot the first 1,000 steps. (1 point)

```{r}
step <- c(0)
for(i in 1:10000){
  coin_flip <- sample(c(1,-1),1)
  step[i+1]<- step[i]+ coin_flip
}


plot(step[1:1000])

```
Confidence = 0

# Problem 4

What was the most positive and most negative step reached out of 10,000? (1 point)
```{r}
max(step)
min(step)
```

confidence = 100 

# Problem 5

What was the longest run of steps where all steps were positive numbers. For example, in the sequence: 1,2,3,2,1,0,-1,-2,-1,-2,-1,0,1,2,3; the answer is 5 because the first five values were all positive, and this was the longest sequence of positive values. (1 point).

```{r}
logical_step <- sign(step)

sequence <- c()
counter <- 0
for( i in 1:length(logical_step)){
 if(logical_step[i] == 0){
   sequence <- c(sequence,counter)
   counter <- 0
 } else {
     counter <- counter+logical_step[i]
   }
}

max(sequence)
```

confidence = 0




