---
title: "Lab 8"
author: "Kristina Arevalo"
date: '`r format(Sys.time(), "%a %b %d %Y")`'
output: 
  pdf_document:
    toc: yes 
    toc_depth: 2
monofont: Times New Roman
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE)
```

```{r,echo=FALSE}
library(dplyr)
library(ggplot2)
```

\newpage

# Problem 1
Write a function to convert a vector of raw-scores into z-scores. The function should have inputs for the vector, the mean and sd of the normal distribution, and should return a vector of zscores. (1 point).
*Also, demonstrate that the function works correctly (1 point). How you make the demonstration is up to you.

```{r}
convert_to_z_score <- function(score,mean,sd){
  z_scores <- (score-mean)/sd
return(z_scores)
}

raw_scores<- c(85,76,91,65,88)
convert_to_z_score(raw_scores, 75, 2)


```
confidence=100

# Problem 2

Base R does not have a function for a z-test. Write a function to accomplish a one-sample z-test. Remember, a one-sample z test is used to compare the probability of obtaining the sample mean (or larger or smaller) if it came from a known normal distribution. (2 points).

*Use your z-test function to conduct a test of the following. A sample of 25 scores is taken. The mean of the sample is 50. The sample is assumed to have been taken from a normal distribution with mean 40 and standard deviation 7. 
*Report a one-tailed z-test, examining the probability of obtaining a sample of greater than 50 in this situation. Report the results, and give a brief sentence explaining the result and the inference you make (2 points).

```{r}
z_test <- function(sample_mean, sample_size, mu, sigma){
  sample_dist_mean <- mu
  sample_dist_sd <- sigma/(sqrt(sample_size))
  
  p_value <- pnorm(sample_mean, sample_dist_mean, sample_dist_sd, lower.tail = FALSE)
  return (p_value)
}

z_test(sample_mean = 50, 
       sample_size = 25, 
       mu= 40, 
       sigma = 7)
  
```

Given this information, the value of is p is very small or p < .001 and it would be improbable to obtain a sample of greater than 50 with these values. 

confidence= 50 

