---
title: "Lab 1"
author: "Kristina Arevalo"
date: '`r format(Sys.time(), "%a %b %d %Y")`'
output: 
  pdf_document:
monofont: Times New Roman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Problem 1
## Compute the sum of the sequence 100 to 1000, going up by a constant value of 100
```{r}
sum(seq(100,1000,100))

```

# Problem 2
## Compute the sum of these numbers, (1,3,2,4,3,5,4,3,4,5,6,5,6,7,6,5,6,5,4,3,4,5)
```{r}
sum(c(1,3,2,4,3,5,4,3,4,5,6,5,6,7,6,5,6,5,4,3,4,5))
```

# Problem 3
## Write a custom sequence generator function using a for loop that generates a sequence from a starting integer value to an ending integer value in steps of 1. Demonstrate that it can produce the sequence 1 to 10.

```{r}
seq_gen <- function(start,end) {
  for(i in start:end){
    print(i)
  }
}

seq_gen(1,10)
```

# Problem 4
## Write a custom function to implement the following general equation to find the sum of any constant series:

## Demonstrate that your function correctly produces the sum for the series below: seq(10,100,10)
#>  [1]  10  20  30  40  50  60  70  80  90 100

```{r}

const_series <- function(X1, Xn, step) 
  {
  (((Xn-X1)/step) + 1) * ((X1+Xn)/2)
}
const_series(10, 100, 10)
```













