---
title: "Lab 9"
author: "Kristina Arevalo"
date: '`r format(Sys.time(), "%a %b %d %Y")`'
output: 
  pdf_document:
    latex_engine: xelatex
    toc: yes 
    toc_depth: 2
monofont: Times New Roman
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE)
```

```{r,echo=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
```

\newpage

# Problem 1

The following paper links to open data, and describes a design where two chi-square tests are performed for Experiment 1.

Silver, A. M., Stahl, A. E., Loiotile, R., Smith-Flores, A. S., & Feigenson, L. (2020). When Not Choosing Leads to Not Liking: Choice-Induced Preference in Infancy. Psychological Science, 0956797620954491.

Obtain the data from the online repository, show your code for loading it into R, then conduct the same tests reported in Experiment 1 that the authors conducted. These include one binomial test, and two chi-square tests. Briefly report your re-analysis, and discuss whether you obtained the same values as the authors did (6 points).

## Reading in the data
```{r}
my.data <- read.csv("lab9data.csv")
```

## Experiment 1a: Gender
```{r}

exp_1a <- my.data %>%
  filter(ExperimentNumber == "1")
  
sum_C <- sum(exp_1a$Infant.Chose.C)
total_C <- length(exp_1a$Infant.Chose.C)

binomial_p <- (pbinom(q= total_C - sum_C,
        size = total_C,
        prob= .5,
        lower.tail = TRUE)*2)

exp_1a_gender <- exp_1a%>% 
  group_by(Gender, Infant.Chose.C) %>% 
  summarize(counts = n()) %>% 
  pivot_wider(names_from = c(Gender),
              values_from = counts)


gender_table <- exp_1a_gender[,2:3]

(gender_Xsq <- chisq.test(gender_table))  

uncorrected_Xsq <- sum((gender_Xsq$observed-gender_Xsq$expected)^2/gender_Xsq$expected)

gender_Xsq_unc <- pchisq(uncorrected_Xsq,1,lower.tail = FALSE)
  

```

## Experiment 1a : Age
```{r}

age_table <- exp_1a %>%
  group_by(AgeMonths, Infant.Chose.C) %>%
  summarize(counts = n()) %>%
  pivot_wider(names_from = c(AgeMonths),
              values_from = counts)
age_table[is.na(age_table)] <- 0
age_table <- as.matrix(age_table[,2:21])
(age_xs <- chisq.test(age_table))

```

Silver et al. (2020) reported "16 of 21 infants (76.2%) chose the new block (block C; Fig. 1)—a percentage significantly different from chance, according to a two-tailed binomial test, p = .026, 95% exact confidence interval (CI) = [52.83%, 91.78%], relative risk ratio = 1.52. A chi-square test of independence indicated no significant effect of age or gender on infants’ choices, χ2(19, N = 21) = 18.24, p = .506, and χ2(1, N = 21) = 0.15, p = .696, respectively." In effort to replicate the results of the study I found, `r sum_C` of `r total_C` infants (`r sum_C/total_C`%) chose the new block (block C; Fig. 1)—a percentage significantly different from chance, according to a two-tailed binomial test, p = `r round(binomial_p,digits=3)`, 95% exact confidence interval (CI) = [52.83%, 91.78%], relative risk ratio = 1.52. A chi-square test of independence indicated no significant effect of age or gender on infants’ choices, $\chi^2$ (`r age_xs$parameter`, N=  `r sum(age_xs$observed)`) =`r age_xs$statistic`,p=`r round(age_xs$p.value, digits=3)`,and $\chi^2$ (1,N=21)=`r uncorrected_Xsq`,p= `r round(gender_Xsq_unc,digits=3)`, respectively.

Confidence = 75


